\textsc{\wobble: a data-driven method for precision radial velocities}

### 2019-01-02 paper/paper.tex

\software{%
    astropy \citep{Astropy13, Astropy18},
    numpy \citep{Van-Der-Walt:2011},
    matplotlib \citep{Hunter:2007},
    scipy \citep{Jones:2001},
    tensorflow \citep{Abadi15}, 
    exoplanet \citep{exoplanet},
    starry \citep{Luger2018}
}

>>>>

\software{%
    astropy \citep{Astropy13, Astropy18},
    numpy \citep{Van-Der-Walt:2011},
    matplotlib \citep{Hunter:2007},
    scipy \citep{Jones:2001},
    tensorflow \citep{Abadi15}, 
    exoplanet \citep{exoplanet},
    starry \citep{Luger2018},
    pymc3 \citep{pymc3},
    theano \citep{theano}
}
